Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
Introduction ter.

Finally, we show that these complexes have very nice combinatorial properties.

@@

\section{Properties of the non-crossing and non-kissing complexes}

>>>>

Finally, we show in Section \ref{sec:propertiesOfComplexes} that these complexes are combinatorially very well-behaved.

@@

\section{Properties of the non-crossing and non-kissing complexes}\label{sec:propertiesOfComplexes}
